Approximation as Differentiation notes

### 2025-03-04 notes/sec/grothendieck.tex
Standardise x, y for indices instead of i, j.
Revert to point-free for reindexing functions.
And express biproduct injections as morphisms in Fam(I,C) rather than families of morphisms in C.
Dang, no that doesn't work.

\begin{enumerate}
\item $[X, Y]$ to be the object in $\Fam(C)$ with $\idx{[X,Y]} = \Fam(C)(X,Y)$ and $\faml{[X, Y]}(f) =
\prod_{\idx{X}}\reindex{\faml{Y}}{\idx{f}}$ for every $f: X \to Y$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) sending any $f: X \times Y \to Z$ to
$\lambda_{X,Y,Z}(f): X \to [Y, Z]$ with:
\begin{itemize}
\item $\idx{\lambda}_{X,Y,Z}(f)(i) = g$ where $\idx{g}(j) = \idx{f}(i, j): \idx{Y} \to \idx{Z}$ and
$\faml{g}(j) = \faml{f}_{i,j} \comp \inj_{\faml{Y}_j}: \faml{Y}_i \to \faml{Z}_{\idx{f}(i, j)}$ where
$\inj_{\faml{Y}_j}: \faml{Y}_j \to \faml{X}_i \biprod \faml{Y}_j$
\item $\faml{\lambda}_{X,Y,Z}(f)(i) = \lambda_{\prod_{\idx{Y}}}(j \mapsto \faml{f}_{i, j} \comp
\inj_{\faml{X}_i}: \faml{X}_i \to \faml{Z}_{f(i,j)}$ where $\inj_{\faml{X}_i}: \faml{X}_i \to \faml{X}_i
\biprod \faml{Y}_j$)
\end{itemize}
\item The family of morphisms $\eval_{X,Y}: [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $\idx{\eval}_{X,Y}(f, i) = \idx{f}(i)$
\item $\faml{\eval}_{X,Y}(f, i) = \coprodM{{\eval_{\prod}}_i}{\faml{f}_i}:
\prod_{\idx{X}}\reindex{\faml{Y}}{f} \biprod \faml{X}_i \to \faml{Y}_{\idx{f}(i)}$
\end{itemize}
using $\coprodM{-}{-}$ to denote coproduct of morphisms.
\end{enumerate}
Then for any $f: X \times Y \to Z$ in $\Fam(C)$ we have:
\begin{enumerate}
\item To show that the diagram on the left in $\Fam(C)$ commutes, it suffices to show that the diagram on the
right in $C$ commutes for every $(x, y) \in \idx{X} \times \idx{Y}$:

>>>>

\begin{enumerate}
\item $[X, Y]$ to be the object in $\Fam(C)$ with $\idx{[X,Y]} = \Fam(C)(X,Y)$ and $\faml{[X, Y]}(f) =
\prod_{\idx{X}}\reindex{\faml{Y}}{\idx{f}}$ for every $f: X \to Y$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) sending any $f: X \times Y \to Z$ to
$\lambda_{X,Y,Z}(f): X \to [Y, Z]$ with:
\begin{itemize}
\item $\idx{\lambda}_{X,Y,Z}(f)(x) = g$ where $\idx{g} = \idx{f} \comp (x, -): \idx{Y} \to \idx{Z}$ and
$\faml{g} = \faml{f} \comp \inj_{\faml{Y}}: \faml{Y} \to \reindex{\faml{Z}}{\idx{g}}$ where $\inj_{\faml{Y}}:
\faml{Y} \to \const_{\idx{Y}}(\faml{X}_x) \biprod \faml{Y}$
\item $\faml{\lambda}_{X,Y,Z}(f)(x) = \lambda_{\prod_{\idx{Y}}}(\faml{f} \comp \inj_{\faml{X}_x}:
\const_{\idx{Y}}(\faml{X}_x) \to \reindex{\faml{Z}}{f}$ where $\inj_{\faml{X}_x}: \const_{\idx{Y}}(\faml{X}_x)
\to \const_{\idx{Y}}(\faml{X}_x) \biprod \faml{Y}$)
\end{itemize}
\item The family of morphisms $\eval_{X,Y}: [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $\idx{\eval}_{X,Y}(f, x) = \idx{f}(x)$
\item $\faml{\eval}_{X,Y}(f, x) = \coprodM{{\eval_{\prod}}_x}{\faml{f}_x}:
\prod_{\idx{X}}\reindex{\faml{Y}}{f} \biprod \faml{X}_x \to \faml{Y}_{\idx{f}(x)}$
\end{itemize}
using $\coprodM{-}{-}$ to denote coproduct of morphisms.
\end{enumerate}
Then for any $f: X \times Y \to Z$ in $\Fam(C)$ we have the following.
\begin{enumerate}
\item The diagram on the left in $\Fam(C)$ commutes; it suffices to show that the diagram on the right in $C$
commutes for every $(x, y) \in \idx{X} \times \idx{Y}$:
